Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-12-19 presentations/illustrations/attacks.tex
Presentation illustrations: move text slide to main file.
Presentation illustrations: tune attack 3 slide to remove confusion about heap vs code memory.

\begin{frame}
  \frametitle{Stack Capabilities Problems}
  \begin{itemize}
  \item Stack capabilities are not a panacea
  \item Stack pointers must not leave stack frame (through memory or stack)
  \item Similar problems for return pointers (omitted)
  \item Solution: local capabilities?
    \begin{itemize}
    \item Make stack and return capabilities local
    \item Cannot leave registers (except on stack) (\sout{Attack 1})
    \item Stack clearing on boundary crossings (\sout{Attack 2})
    \end{itemize}
  \end{itemize}
\end{frame}

\begin{frame}
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    \frametitle{Stack and return capabilities: Attack 3}
    \begin{scope}
    \clip (-.1,-.1) rectangle (5.1,10.1);
    \fill[fill=gray!50] (0,0) rectangle (5,10);
    \draw (0,0) -- (0,10);
    \draw (5,0) -- (5,10);
    \end{scope}
    \draw (2.5,11) node {heap memory};

    \begin{scope}
    \clip (12.9,-.1) rectangle (18.1,11.1);
    \fill[fill=gray!50] (13,0) rectangle (18,11);
    \draw (13,0) -- (13,11);
    \draw (18,0) -- (18,11);
    \end{scope}
    \draw (15.5,12) node {more heap memory};

@@

\note{Callee has access to some place to store things.}
    \begin{onlyenv}<+->
      \draw[fill=gray!30] (0,1) rectangle (5,4) node[pos=.5] {\footnotesize caller code};
      \draw[fill=white] (13,3) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
      \draw[fill=white] (13,1) rectangle (18,1.5) node[pos=.5] {};
    \end{onlyenv}

    \begin{onlyenv}<.-.(2)>
      \draw [decorate,decoration={brace,amplitude=2pt,mirror,raise=4pt},yshift=0pt]
      (18.1,1) -- (18.1,1.5) node[draw=black] (copy) [black,midway,xshift=0.5cm] {};
      \draw (18,4.75)  edge[->,bend left] (copy);
    \end{onlyenv}

@@

\note{Callee calls callee (1)}
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=10pt,raise=4pt},yshift=0pt]
      (12.9,3) -- (12.9,6) node[draw=black] (ret2) [black,midway,xshift=-0.8cm] {};
      \draw node[fill=gray!50,left=0cm of ret2] { \phantom{ret-ptr (1)} };
      \draw node[left=0cm of ret2] { ret-ptr (1) };
    \end{onlyenv}

    \begin{onlyenv}<+->
      \draw[fill=white] (0,5) rectangle (5,8) node[pos=.5] {\footnotesize callee code (1)};
      \draw[fill=gray!30] (13,3) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
      \draw[fill=gray!30] (13,1) rectangle (18,1.5) node[pos=.5] {\scriptsize {\color{red} copy of ret-ptr}};
    \end{onlyenv}

\note{Callee (1) calls callee (2)}
    \begin{onlyenv}<+->
      \capbrace[ret3]{(5.1,5)}{(5.1,8)}
      \draw node[fill=gray!50,right=0cm of ret3] { \phantom{ret-ptr (2)} };
      \draw node[right=0cm of ret3] { ret-ptr (2) };
    \end{onlyenv}

@@

\note{This breaks well-bracketedness as ret-ptr (2) and ret-ptr (1) was not returned to}
    \begin{onlyenv}<+->
      \draw (9,5.5) node [ellipse, draw, red, thick,minimum height=1.5cm, minimum width=3cm] { };
      \draw node[red,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (12,10) { These were skipped!};  
    \end{onlyenv}
  \end{tikzpicture}
\end{frame}
%%% Local Variables:
%%% TeX-master: "presentation-illustrations"
%%% End:

>>>>

\begin{frame}
  \begin{tikzpicture}[scale=.5, every node={scale=.5}]
    \frametitle{Stack and return capabilities: Attack 3}
    \begin{scope}
    \clip (-.1,-.1) rectangle (5.1,10.1);
    \fill[fill=gray!50] (0,0) rectangle (5,10);
    \draw (0,0) -- (0,10);
    \draw (5,0) -- (5,10);
    \end{scope}
    \draw (2.5,11) node {code memory};

    \begin{scope}
    \clip (12.9,3.9) rectangle (18.1,11.1);
    \fill[fill=gray!50] (13,4) rectangle (18,11);
    \draw (13,4) -- (13,11);
    \draw (18,4) -- (18,11);
    \end{scope}
    \draw (15.5,12) node {more code memory};

    \begin{scope}
    \clip (12.9,-.1) rectangle (18.1,2.1);
    \fill[fill=gray!50] (13,0) rectangle (18,2);
    \draw (13,0) -- (13,2);
    \draw (18,0) -- (18,2);
    \end{scope}
    \draw (15.5,3) node {heap memory};

@@

\note{Callee has access to some place to store things.}
    \begin{onlyenv}<+->
      \draw[fill=gray!30] (0,1) rectangle (5,4) node[pos=.5] {\footnotesize caller code};
      \draw[fill=white] (13,5) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
      \draw[fill=white] (13,1) rectangle (18,1.5) node[pos=.5] {};
    \end{onlyenv}

    \begin{onlyenv}<.-.(2)>
      \draw [decorate,decoration={brace,amplitude=2pt,mirror,raise=4pt},yshift=0pt]
      (18.1,1) -- (18.1,1.5) node[draw=black] (copy) [black,midway,xshift=0.5cm] {};
      \draw (18,5.5)  edge[->,bend left] (copy);
    \end{onlyenv}

@@

\note{Callee calls callee (1)}
    \begin{onlyenv}<+->
      \draw [decorate,decoration={brace,amplitude=3pt,raise=4pt},yshift=0pt]
      (12.9,5) -- (12.9,6) node[draw=black] (ret2) [black,midway,xshift=-0.8cm] {};
      \draw node[fill=gray!50,left=0cm of ret2] { \phantom{ret-ptr (1)} };
      \draw node[left=0cm of ret2] (retptr1) { ret-ptr (1) };
    \end{onlyenv}

    \begin{onlyenv}<+->
      \draw[fill=white] (0,5) rectangle (5,8) node[pos=.5] {\footnotesize callee code (1)};
      \draw[fill=gray!30] (13,5) rectangle (18,6) node[pos=.5] {\footnotesize callee code};
      \draw[fill=gray!30] (13,1) rectangle (18,1.5) node[pos=.5] {\scriptsize {\color{red} copy of ret-ptr}};
    \end{onlyenv}

\note{Callee (1) calls callee (2)}
    \begin{onlyenv}<+->
      \capbrace[ret3]{(5.1,5)}{(5.1,8)}
      \draw node[fill=gray!50,right=0cm of ret3] { \phantom{ret-ptr (2)} };
      \draw node[right=0cm of ret3] (retptr2) { ret-ptr (2) };
    \end{onlyenv}

@@

\note{This breaks well-bracketedness as ret-ptr (2) and ret-ptr (1) was not returned to}
    \begin{onlyenv}<+->
      \draw node [ellipse, fit=(retptr1) (retptr2), draw, red] { };
      \draw node[red,cloud,cloud puffs=10.8,cloud puff arc=110, aspect=3, draw, fill=white, align=center] () at (12,10) { These were skipped!};  
    \end{onlyenv}
  \end{tikzpicture}
\end{frame}
%%% Local Variables:
%%% TeX-master: "presentation-illustrations"
%%% End:
